Quick, Draw! Image Classification

### 2018-12-08 report/draft.tex
updating section 3.3.2

Most modern neural networks are trained using maximum likelihood. This
means that the cost function is the negative log-likelihood, also
described as the cross-entropy between the training data and the model
distribution \cite{Goodfellow-et-al-2016}. In our use case, we are interested
in correctly classifying 10 categories of drawings. Our output unit
use a Softmax function in our output layer because they are most often
used for classifiers representing the probability distribution over
$n$ different classes. Given features $h$, weights $W$, and bias $b$, a
linear layer first predicts unnormalized log probabilities:
\begin{equation}
  z = W^Th + b 
\end{equation}

@@

\begin{enumerate}
\item \textbf{Convolution:} Convolution operation helps to extract features
  from the input image. The ﬁrst argument to the convolution is often referred
  to as the input , the second argument as the feature detector (kernel) and
  the output as the feature map. The convolution operation takes the dot
  product of feature map and the input to detect features. Since each
  convolution operation only focuses on a part of an image enabling parameter
  sharing which helps to reduce the number of free parameters compared to a
  fully connected neural network, allowing the network to be deeper with
  fewer parameters.

  \begin{itemize}
  \item \textbf{Strides:} Stride is the number of pixels jumps between
    each convolution operation performed on the input matrix. When the stride
    is 1 then we move the filters to 1 pixel at a time. Increasing the stride
    parameter reduces the output volume of the convolution since the jumps
    are larger.
  \item \textbf{Padding:}Padding helps to detect features present at the
    border by adding a dummy values around the edge. Since convolution
    operations collect most information from the center of the image, adding
    padding allows the border pixels to be weighed more during the convolution
    operation.
  \end{itemize}

@@

\item \textbf{Fully Connected Layer:} The layer we call as FC layer, we
  flattened our matrix into vector and feed it into a fully connected layer
  like neural network.
  \end{enumerate}

@@

Our analysis required us to use a subset of this data. Our dataset sample
selected for this experiment had 10 categories: fish, fork, hotdog, flamingo,
airplane, alarm clock, baseball bat, bicycle, dolphin, elephant. We had
100,000 examples in total, with 10,000 example for each of the aforementioned
categories.

@@

As found in the experiments, after decreasing the amount of data resulted
in overfitting thereby confirming our hypothesis. Figure \ref{fig:h3Results}
contains a table with results for various number $n$ of observations.
We increased the number of categories the Neural Network had to model,
holding the number of examples per categories constant. Observations were
increased in steps of 1,000 from $n=7000$ to $n=20,000$ examples. The
number of categories $k$ ranged from $k=3$ to $k=10$ in steps of 1.

@@

Results can be seen in the Appendix with Figure \ref{fig:h4Results}.
Increasing the number of categories will cause a significant drop in the
performance of the neural network. Increasing the overall data points for
the network to be trained on should help.

We try and understand the limits and capacity of the finalized model by
varying the number of categories and the number of rows per category. We
then measure the response accuracy and response loss of the model. The
number of rows per category is altered in steps of 1000 from 7,000 to 20,000
and the number of categories is altered in steps of 1 from 3 to 10.

3 examples of the accuracy measurements with most rows (14,000), least rows
(2,000) and intermediate rows (7,000) and their performance per every
additional category is plotted below.

>>>>

Most modern neural networks are trained using maximum likelihood. This
means that the cost function is the negative log-likelihood, also
described as the cross-entropy between the training data and the model
distribution \cite{Goodfellow-et-al-2016}. In our use case, we are interested
in correctly classifying 10 categories of drawings. Our output layer
uses a Softmax function to represent the probability distribution over
$k$ different classes. Given features $h$, weights $W$, and bias $b$, a
linear layer first predicts unnormalized log probabilities:
\begin{equation}
  z = W^Th + b 
\end{equation}

@@

\begin{enumerate}
\item \textbf{Convolution:} The convolution operation helps to extract features
  from the input image. The first argument is often referred
  to as the input. The second is a feature detector (kernel) and
  the output is the feature map. The convolution operation takes the dot
  product of the feature detector and the input. Each convolution operation
  focuses on a subset of an image. This approach allows for parameter
  sharing which leads to a reduction in parameters relative to a
  fully connected neural network. The advantage 
  is that we can have a deeper network with fewer parameters.

  \begin{itemize}
  \item \textbf{Strides:} Stride is the number of pixels jumps between
    each convolution operation performed on the input matrix. When the stride
    is 1 then we move the filters to 1 pixel at a time. Increasing the stride
    parameter reduces the output volume of the convolution since the jumps
    are larger.
  \item \textbf{Padding:} Padding helps to detect features present at the
    border by adding a dummy values around the edge. Since convolution
    operations collect most information from the center of the image, adding
    padding allows the border pixels to be weighed more during the convolution
    operation.
  \end{itemize}

@@

\item \textbf{Fully Connected (FC) Layer:} The FC layer flattens our
  matrix into vector and feeds it into a fully connected neural network layer.
  \end{enumerate}

@@

Our analysis required us to use a subset of this data. Our dataset sample
selected for this experiment had 10 categories: fish, fork, hotdog, flamingo,
airplane, alarm clock, baseball bat, bicycle, dolphin, elephant. We had
100,000 examples in total, with 10,000 examples for each of the aforementioned
categories.

@@

As found in the experiments, decreasing the amount of data resulted
in overfitting thereby confirming our hypothesis. Figure \ref{fig:h3Results}
contains a table with results for various number $n$ of observations. We
can see in Figure \ref{fig:h3Results} that increasing the number of
observations enables us tune a well-trained model.

@@

We found that imbalanced class prediction can be improved by adding more
data to the minority class. As shown in Figure \ref{fig:h4Results},

shows us that

a
decrease in class imbalance leads to an increase in prediction accuracy
for the minority class. These predictions were based on 20,000 total
samples which were previously unseen.
